Tropopause Evolution in a Rapidly Intensifying Tropical Cyclone: A Static Stability Budget Analysis

### 2017-12-07 paper.tex
Added static stability tendency equation and some description to Budget Computation section.

The static stability can be expressed as the squared Brunt V{\"a}is{\"a}l{\"a} frequency:
   \begin{equation} \label{eq:n2moist}
   N_m^2 = \frac{g}{T}(\frac{\partial T}{\partial z}+\Gamma_m)(1+\frac{T}{R_d/R_v+q_s}\frac{\partial q_s}{\partial T})-\frac{g}{1+q_t}\frac{\partial q_t}{\partial z},
   \end{equation}
where g is gravitational acceleration, T is temperature, $R_d$ and $R_v$ are the gas constants of dry air and water vapor, respectively, $q_s$ is the saturation mixing ratio, and $q_t$ is the total condensate mixing ratio. $Gamma_m$ is the moist-adiabatic lapse rate:
   \begin{equation} \label{eq:gamma_m}
   \Gamma_m = DETERMINE WHAT THIS IS FOR THE NON-CONSERVATIVE EQUATION SET
   \end {equation}
In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
   \begin{equation} \label{eq:n2dry}
   N^2 = \frac{g}{\theta_v}\frac{\partial \theta_v}{\partial z},
   \end{equation}
where \textit{g} is gravitational acceleration and $\theta_v$ is the virtual potential temperature.
To compute $N^2$, CM1 uses Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in unsaturated environments; for mathematical simplicity, however, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.

Taking the time derivative of Eq. \ref{eq:n2dry} yields the static stability tendency:
   \begin{equation} \label{eq:dn2dt}
   \

The potential temperature tendency can be partitioned into ### "budget variables," which are output directly by the model every two minutes:

POTENTIAL TEMPERATURE TENDENCY EQUATION

 \section{Results}

>>>>

The static stability can be expressed as the squared Brunt V{\"a}is{\"a}l{\"a} frequency:
   \begin{equation} \label{eq:n2moist}
   N_m^2 = \frac{g}{T}(\frac{\partial T}{\partial z}+\Gamma_m)(1+\frac{T}{R_d/R_v+q_s}\frac{\partial q_s}{\partial T})-\frac{g}{1+q_t}\frac{\partial q_t}{\partial z},
   \end{equation}
where g is gravitational acceleration, T is temperature, $R_d$ and $R_v$ are the gas constants of dry air and water vapor, respectively, $q_s$ is the saturation mixing ratio, and $q_t$ is the total condensate mixing ratio. $\Gamma_m$ is the moist-adiabatic lapse rate:
   \begin{equation} \label{eq:gamma_m}
   \Gamma_m = DETERMINE WHAT THIS IS FOR THE NON-CONSERVATIVE EQUATION SET
   \end {equation}
In the tropopause layer, $q_s$, $\frac{\partial q_s}{\partial T}$, and $\frac{\partial q_t}{\partial z}$ approach zero. In this limiting case, Eq. \ref{eq:n2moist} reduces to:
   \begin{equation} \label{eq:n2dry}
   N^2 = \frac{g}{\theta_v}\frac{\partial \theta_v}{\partial z},
   \end{equation}
where \textit{g} is gravitational acceleration and $\theta_v$ is the virtual potential temperature.
To compute $N^2$, CM1 uses Eq. \ref{eq:n2moist} in saturated environments and Eq. \ref{eq:n2dry} in unsaturated environments; for mathematical simplicity, however, only Eq. \ref{eq:n2dry} will be used for the budget computations herein\footnote{The validity of this approximation will be substantiated later in this section.}.

Taking the time derivative of Eq. \ref{eq:n2dry} yields the static stability tendency:
   \begin{equation} \label{eq:dn2dt}
   \frac{\partial N^2}{\partial t} = \frac{g}{\theta}\frac{\partial}{\partial z}\frac{\partial \theta}{\partial t}+\frac{g}{\theta^2}\frac{\partial \theta}{\partial z}\frac{\partial \theta}{\partial t},
   \end{equation}
where the potential temperature tendency, $\frac{\partial \theta}{\partial z}$, is:
   \begin{equation} \label{eq:dthetadt}
   \frac{\partial \theta}{\partial t} = 
   \end{equation}
Each term on the right-hand side of Eq. \ref{eq:dthetadt} represents a potential temperature budget variable, each of which is output directly by the model every minute.
These tendencies are substituted for $\frac{\partial \theta}{\partial t}$ in Eq. \ref{eq:dn2dt}, yielding the static stability tendency attributable to each budget term every minute.
 \section{Results}
